---
title: "Practicum"
author: "Kavish"
date: "9/19/2018"
output: html_document
---

Question to Solve : Readmission Prediction in diabetes patients ??

Dataset: The dataset represents 10 years (1999-2008) of clinical care at 130 US hospitals.
and integrated delivery networks. It includes over 50 features representing 
patient and hospital outcomes.

Source: https://archive.ics.uci.edu/ml/datasets/Diabetes+130-US+hospitals+for+years+1999-2008


```{r setup, include=FALSE}
library(dplyr)
library(GGally)
library(ggplot2)
library(corrplot)
library(psych)
library(caret)
library(rpart)
library(randomForest)
library(nnet)
library(e1071)
library(ROCR)
library(CORElearn)
library(lasso2)
```

## R Markdown

1.Load Data
2.Clean Data (By Looking at data and Domain Knowledge #remove unnecessary columns)

```{r cars}
filename <- 'diabetic_data.csv'
diabetic_data <- read.table(filename, sep = ",", header = T, na.strings = "?")
head(diabetic_data)
dim(diabetic_data)
clean_diabetic_data <- select(diabetic_data,-encounter_id,-patient_nbr,-weight,-diag_1,-diag_2,-diag_3,-(25:41),-(43:47))
dim(clean_diabetic_data)
head(clean_diabetic_data)
```

1.Summary 
2.Replace NA Values with Other

```{r}
summary(clean_diabetic_data)
clean_diabetic_data$race[is.na(clean_diabetic_data$race)] <- "Other"
any(is.na(clean_diabetic_data$race))
clean_diabetic_data$payer_code <- as.character(clean_diabetic_data$payer_code)
clean_diabetic_data$payer_code[is.na(clean_diabetic_data$payer_code)] <-"Other"
clean_diabetic_data$payer_code <- as.factor(clean_diabetic_data$payer_code)
any(is.na(clean_diabetic_data$payer_code))
clean_diabetic_data$medical_specialty <- as.character(clean_diabetic_data$medical_specialty)
clean_diabetic_data$medical_specialty[is.na(clean_diabetic_data$medical_specialty)] <- "Other"
clean_diabetic_data$medical_specialty <- as.factor(clean_diabetic_data$medical_specialty)
any(is.na(clean_diabetic_data$medical_specialty))
```

## Including Plots

Some Preliminary Analysis using Box Plot for readmitted cases.

```{r pressure, echo=FALSE}
g <- ggplot(clean_diabetic_data, aes(x=race, y=time_in_hospital))
g + geom_boxplot(aes(fill=readmitted))
```




```{r}
g <- ggplot(clean_diabetic_data, aes(x=age, y=time_in_hospital))
g + geom_boxplot(aes(fill=readmitted))
```


```{r}
g <- ggplot(clean_diabetic_data,aes(x=A1Cresult, y=time_in_hospital))
g + geom_boxplot(aes(fill=diabetesMed)) + facet_grid(. ~ readmitted)
```


Converting into factors with bit of Domain Knowledge... from ID Mapping Table.

```{r}
clean_diabetic_data_new <- clean_diabetic_data
clean_diabetic_data_new$admission_type<- factor( rep("other",nrow(clean_diabetic_data_new)),ordered = F, 
                             levels = c("Elective","Emergency","Other"))
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==1]<- "Emergency"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==2]<- "Emergency"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==3]<- "Elective"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==4]<- "Other"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==5]<- "Other"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==6]<- "Other"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==7]<- "Emergency"
clean_diabetic_data_new$admission_type[clean_diabetic_data_new$admission_type_id==6]<- "Other"
```



```{r}
clean_diabetic_data_new$discharge_disposition_type<-factor(rep("other",nrow(clean_diabetic_data_new)),ordered = F,levels = c("Home","Hospital","Other"))

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==1 ]<-"Home"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==2]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==3]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==4]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==5]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==6 ]<-"Home"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==7 ]<-"Home"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==8]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==9]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==10]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==11]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==12]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==13 ]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==14]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==15]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==16]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==17]<-"Hospital"


clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==18]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==19]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==20]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==21]<-"Expired"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==22]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==23]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==24]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==25]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==26]<-"Other"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==27]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==28]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==29]<-"Hospital"

clean_diabetic_data_new$discharge_disposition_type[clean_diabetic_data_new$discharge_disposition_id==30]<-"Hospital"

head(clean_diabetic_data_new)

```



```{r}
clean_diabetic_data_new$admission_source_type<-factor(rep("other",nrow(clean_diabetic_data_new)),ordered = F,levels = c("Transfer","Referal","Other"))

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==1]<-"Referal"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==2]<-"Referal"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==3]<-"Referal"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==4]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==5]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==6]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==7]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==8]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==9]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==10]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==11]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==12]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==13]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==14]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==15]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==17]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==18]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==19]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==20]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==21]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==22]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==23]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==24]<-"Transfer"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==25]<-"Other"

clean_diabetic_data_new$admission_source_type[clean_diabetic_data_new$admission_source_id ==26]<-"Other"

clean_diabetic_data_final <- select(clean_diabetic_data_new, -payer_code,-admission_source_id,-admission_type_id,-discharge_disposition_id,-medical_specialty)
head(clean_diabetic_data_final)

```
Training and Test Data Partitioning..

```{r}
set.seed(123)
inTrain <- createDataPartition(y = clean_diabetic_data_final$readmitted, p = .7,list = FALSE)
train <- clean_diabetic_data_final[ inTrain,]
test <- clean_diabetic_data_final[-inTrain,]
nrow(train) 
nrow(test)
```

Logistic regression with preliminary cleaned Data

```{r}
fit_1 <- glm(readmitted ~., data=train, family=binomial)
summary(fit_1)
```

Diagnosis Tests...


```{r}
logisticPseudoR2s <- function(LogModel) {
  dev <- LogModel$deviance 
  nullDev <- LogModel$null.deviance 
  modelN <-  length(LogModel$fitted.values)
  R.l <-  1 -  dev / nullDev
  R.cs <- 1- exp ( -(nullDev - dev) / modelN)
  R.n <- R.cs / ( 1 - ( exp (-(nullDev / modelN))))
  cat("Pseudo R^2 for logistic regression\n")
  cat("Hosmer and Lemeshow R^2  ", round(R.l, 3), "\n")
  cat("Cox and Snell R^2        ", round(R.cs, 3), "\n")
  cat("Nagelkerke R^2           ", round(R.n, 3),    "\n")
}

logisticPseudoR2s(fit_1)
```


Playing with Variables for better Logistic Model..

```{r}
clean_diabetic_data_final2 <- select(clean_diabetic_data_new, -payer_code,-admission_source_id,-admission_type_id,-discharge_disposition_id,-medical_specialty,-gender,-A1Cresult,-number_outpatient,-max_glu_serum,-race,-num_lab_procedures,-change)
set.seed(123)
inTrain <- createDataPartition(y = clean_diabetic_data_final2$readmitted, p = .7,list = FALSE)
train1 <- clean_diabetic_data_final2[ inTrain,]
test1 <- clean_diabetic_data_final2[-inTrain,]
nrow(train1) 
nrow(test1)
fit_1 <- glm(readmitted ~., data=train1, family=binomial)
summary(fit_1)
anova(fit_1, test="Chisq")
```

Discriminant Analysis...

```{r}
predicted <- predict(fit_1, newdata = test1, type = "response")
predicted <- as.numeric(predicted>0.5)
table(predicted,test$readmitted)
```


Final Variables and Diagnosis....


```{r}
clean_diabetic_data_final3 <- select(clean_diabetic_data_new, age,time_in_hospital,num_procedures,number_emergency,number_inpatient,number_diagnoses,insulin,diabetesMed,readmitted)
set.seed(123)
inTrain <- createDataPartition(y = clean_diabetic_data_final3$readmitted, p = .7,list = FALSE)
train2 <- clean_diabetic_data_final3[ inTrain,]
test2 <- clean_diabetic_data_final3[-inTrain,]
nrow(train1) 
nrow(test1)
fit_2 <- glm(readmitted ~., data=train2, family=binomial)
summary(fit_2)
anova(fit_2, test="Chisq")
predicted <- predict(fit_2,test2, type = "response")
predicted <- as.numeric(predicted>0.5)
table(predicted,test2$readmitted)
library(pROC)
predicted <- predict(fit_2, newdata = test2, type = "response")
predicted
roccurve <- roc(test$readmitted ~ predicted)
plot(roccurve)
```

Random Forest and Matrix Diagnosis...


```{r}
Rf_fit<-randomForest(formula=readmitted ~ age+time_in_hospital+
                       +num_procedures+num_medications+number_outpatient+
                       number_emergency+number_inpatient+number_diagnoses+
                       insulin+diabetesMed,
                     data=train)
print(Rf_fit)

test$pred_readmit <- predict(Rf_fit, test, type = "response")
table(test$readmitted, test$pred_readmit)
prop.table(table(test$readmitted, test$pred_readmit),1)
confusionMatrix(test$pred_readmit, test$readmitted)
```


Rpart Tree and Matrix Diagnosis....

```{r}
rpart_tree <- rpart(formula = readmitted ~ age+time_in_hospital+
                      num_procedures+num_medications+number_outpatient+
                      number_emergency+number_inpatient+number_diagnoses+
                      insulin+diabetesMed, 
                    data=train, method = 'class')
summary(rpart_tree)

test$pred_readmit <- predict(rpart_tree, test, type="class")
table(predict(rpart_tree, test, type="class"), test$readmitted)
prop.table(table(test$readmitted, test$pred_readmit),1)
confusionMatrix(test$pred_readmit, test$readmitted)
```

Neural Networks....

```{r}
nnet_model <- nnet(formula = readmitted ~ age+time_in_hospital+
                     num_lab_procedures+num_procedures+num_medications+number_outpatient+
                     number_emergency+number_inpatient+number_diagnoses+
                     insulin+diabetesMed, 
                   data=train, size = 10, maxit = 100)

test$pred_readmit <- predict(nnet_model, test, type = "class")
table(test$readmitted, test$pred_readmit)
```


```{r}

```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
